---
title: "Alcohol vs Seat choice"
author: "Ever De Leon"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

The research question is this: Is there a difference in the average amount of alcohol consumed per week by students who sit in row 1, row 2, or row 3 of the UCDavis classroom.

$H_0$ There is no difference on the average amount of alcohol consumed per week based on seating row.

$H_A$ There is a difference on the average amount of alcohol consumed per week based on seating row.

# Methods

We are trying to predict alcohol consumption based on seating row. 

Data Form UC Davis: 

alcohol ~ Seat

alcohol is a numerical variable

Seat is a categorical variable

So we use the Numerical~cat helper file.

# Description

## Graphical Description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

## Numerical Description 



## Inferential Description

## Conclusions and Discussion


